First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-10 eg6-letters/coherent/dvcs_he4_prl.tex
renaming the GPD models in the CFF plot and cleaning the text

We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
$\mathcal{H}_A$, together with theoretical calculations from two models, 
labelled {\em convolution} and {\em off-shell}. In the convolution 
model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
non-relativistic and non-interacting nucleons, where these nucleons interact 
independently with the probe. The convolution/dual model is based on nucleon 
GPDs from the dual parametrization \cite{Guzey:2006xi}, where the 
convolution/VGG uses nucleon GPDs  from the VGG model and is based on the 
double distributions ansatz \cite{DD_model}. The off-shell model 
\cite{GonzalezHernandez:2012jv} relies on the impulse approximation and uses 
advanced spectral functions of  nuclei that account for all configurations of 
the final nuclear system and the binding effects between the nucleons.
[These need to be renamed on the figure, it does not make sense to call differently
models that are identical. We should also request the projections from Vadim
model: hep-ph/0509158.]

>>>>

We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
$\mathcal{H}_A$, together with theoretical calculations from two models, 
labelled {\em convolution} and {\em off-shell}. In the convolution 
model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
non-relativistic and non-interacting nucleons, where these nucleons interact 
independently with the probe. The Convolution-Dual model is based on nucleon 
GPDs from the dual parametrization \cite{Guzey:2006xi}, where the 
Convolution-VGG uses nucleon GPDs  from the VGG model and is based on the 
double distributions ansatz \cite{DD_model}. The off-shell model 
\cite{GonzalezHernandez:2012jv} relies on the impulse approximation and uses 
advanced spectral functions of  nuclei that account for all configurations of 
the final nuclear system and the binding effects between the nucleons.
